Hierarchical Dispatching and Overriding

### 2017-10-05 NewVersion/sections/Discussion.tex
S5 skeleton

\section{Discussion}
In this section, we discuss the design space and some reflections of the work. 
\paragraph{Abstract Methods.}
Why we include 
\paragraph{Static Invocation.}
Why we include
\paragraph{Method Resolution Rules.}
Other resolution possibilities and comparison.

>>>>

\section{Discussion}
In this section, we discuss the design space and some reflections of the work. 
\paragraph{Abstract Methods.}
Why we include 
\paragraph{Path Invocation}

\paragraph{Static/Super Invocation}
Extensibly adding rules to the current formalization.
- can dispatch to any method (both original method and updating method).
- static dispatch algorithm.

\paragraph{Diamond interface check}

\paragraph{Hierarchical Overriding Restriction.}
In \MIM{}, hierarchical overriding can only override an interface that defines the original method. But in reality, sometimes this condition is too restrict and can be relaxed to allowing overriding a super interface. .. Pros & cons.

\paragraph{Method Resolution Rules.}
Other resolution possibilities and comparison.
